---
title: "Library and Mapping QC"
output: html_document
---
```{r, echo=FALSE}
library(kableExtra)
```

### Part I: Library QC

#### I.I Library removed RNA due to duplicated or substring of other RNAs

**We have `r length(analysis.par$RNA.list)` sh/sgRNAs targeting `r length(unique(analysis.par$lib[,3]))` genes.**

```{r, echo=FALSE}
df<-analysis.par$removed.RNA
kableExtra::kable(df,align = "c") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  kableExtra::scroll_box(width = "100%", height = "500px")
```

#### I.II Distribution of number of RNA targeting per gene

```{r, echo=FALSE, fig.height=7, fig.width=15}
freq_t<-data.frame(rbind(table(analysis.par$lib[,3])))
freq_df<-as.data.frame(t(freq_t))
freq_df$gene<-rownames(freq_df)
rownames(freq_df)<-c()
colnames(freq_df)<-c("n.RNA","gene")
freq_df<-freq_df[,c("gene","n.RNA")]
freq_perc_df<-table(freq_df$n.RNA)*100/sum(table(freq_df$n.RNA))
coul = brewer.pal(5, "Purples")[3]
bar<-barplot(freq_perc_df, col = coul, main = "Number of gRNA target per Gene", ylab = "Percentage %")
neg.info<-paste("Negative control is ", freq_df[freq_df$gene=="control", "n.RNA"])
legend("topleft", legend = neg.info, fill = coul, border = NA, bty = 'n', cex = 1.5)
print(paste("Shuffle n.RNA cutoff is ",names(freq_perc_df)[which.max(freq_perc_df)]))
```

### Part II: Mapping QC

#### II.I Mapping percentage and Coverage.

**We have `r length(analysis.par$sample.names)` samples. **

```{r, echo=FALSE}
df<-analysis.par$raw.summary
df<-plyr::mutate(df,mapping.perc=100*n.matched/total,coverage.seq=round(n.matched/nrow(analysis.par$raw.count.table)))
kableExtra::kable(df,align = "c") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  kableExtra::scroll_box(width = "100%", height = "100%")
```


```{r, echo=FALSE, fig.height=12, fig.width=18}
library(RColorBrewer)
par(mai=c(4,1,1,2))
# First plot is mapping percentage
d<-analysis.par$raw.summary
d$unmapped<-as.numeric(d$total) - as.numeric(d$n.matched)
d<-t(d[,2:4])
colnames(d)<-analysis.par$raw.summary[,1]
d_perc<-apply(d, 2, function(x){return(x*100/x[2])})
coul = brewer.pal(5, "Purples") [2:3]
bar<-barplot(d_perc[c("n.matched", "unmapped"),], col=coul, width = 1, border = NA, names.arg = rep("", ncol(d_perc)))
pp<-par("usr")
#text(x=bar, y=-8, labels = colnames(d), xpd = TRUE, srt=45)
text(x=bar, y=par("usr")[3], srt = 60, adj= 1, xpd = TRUE, labels = colnames(d))
text(x=bar, y = d_perc[1,]/2, labels = paste0(round(d_perc[1,],2),"%"))
text(x=bar, y = d_perc[1,]/2, labels = paste0(round(d_perc[1,],2),"%"))
text(x=bar, y = d_perc[1,] + d_perc[3,]/2, labels = paste0(round(d_perc[3,],2),"%"))
text(x=bar, y = d_perc[1,] + d_perc[3,]/2, labels = paste0(round(d_perc[3,],2),"%"))
legend(x= bar[length(bar)]+0.6, y=pp[4], legend = c("Mapped Reads", "Unmapped Reads"), xpd = TRUE, fill = coul, border = NA, bty = 'n')

```

#### II.II Log2 transformed raw count number distribution across all samples.

```{r, echo=FALSE, fig.height=12, fig.width=18}
par(mai=c(4,1,1,1))
df<-log2(analysis.par$raw.count.table +1)
boxplot(df, col=coul[1], ylab="log2(count+1)", las=2)

```

#### II.III Number of reads with n.mismatch percentage in each sample.
```{r, echo=FALSE, fig.height=12, fig.width=18}
par(mai=c(4,1,1,1))
dist.df<-as.data.frame(analysis.par$raw.count.dist)
dist.df[, 3:ncol(dist.df)]<-sapply(dist.df[,3:ncol(dist.df)], as.numeric)
plot.df<-ddply(dist.df, .(sample), function(df){
  colSums(df[,3:ncol(df)])
})
rownames(plot.df)<-plot.df[,1]
plot.df<-plot.df[,-1]
plot.df.perc<-apply(plot.df, 1, function(x){x*100/sum(x)})
coul = brewer.pal(10, "Set3")
bar<-barplot(plot.df.perc[1:10,], col=coul, border = NA, names.arg = rep("", ncol(d_perc)), ylim=c(0,100), ylab="Percentage %")
abline(h=mean(colSums(plot.df.perc[1:3,])), lty="dotdash", lwd =3)
pp<-par("usr")
text(x=bar, y=pp[3], srt=60, adj=1,xpd=T, labels = colnames(plot.df.perc))
n.mismatch<-seq(0,nrow(plot.df.perc)-1)
legend(x= bar[length(bar)]+0.6, y=pp[4], legend = n.mismatch, xpd = TRUE, fill = coul, border = NA, bty = 'n',title = "n.mismatch", ncol = 2)

```

#### II.IV N.mismatch threshold QC.

```{r, echo=FALSE, fig.height=12, fig.width=18}
n <- 30
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
coul = col_vector[1:20]
sample.num<-dim(plot.df.perc)[2]
par(mfrow=c(round(sqrt(sample.num)),round(sqrt(sample.num))), mar=c(1,5,2,0), oma=c(2,2,1,3))
cutoff<-length(n.mismatch)
for(i in 1:sample.num){
  sub<-plot.df.perc[-c(1,2),i]
  sub<-sub[sub!=0]
  bar<-barplot(sub, col=coul, width=1, border = NA, xlab="", ylab="Percentage %", names.arg = "", main=analysis.par$sample.names[i])
  pp<-par("usr")
  n.mismatch<-gsub("^X","",names(sub))
  legend("topright", legend = n.mismatch, xpd = TRUE, fill = coul, border = NA, bty = 'n',title = "n.mismatch", ncol=2)
  lines(sub)
  threshold<-which(diff(sub,lag=1)>0)
  if(length(threshold)==0){
    pp<-par("usr")
    text(x=median(bar), y=pp[3]-0.02, labels = paste0("Threshold is ", n.mismatch[length(n.mismatch)]), xpd=TRUE, cex = 1.5, col="red")
  } else{
     pp<-par("usr")
    text(x=median(bar), y=pp[3]-0.02, labels = paste0("Threshold is ", n.mismatch[threshold]), xpd=TRUE, cex=1.5, col="red")
    abline(v = which(diff(sub,lag=1)>0), lty="dotted")
    if(threshold[1]<cutoff){
      cutoff<-threshold[1]
    }
    
  }
}
print(paste("Suggested n.mismatch to rescue the most reads is ", min(n.mismatch[cutoff])))
```







